Handling String-Number Conversion in String Constraint Solving

### 2019-11-18 draft.tex

Here both \texttt{x[3]} in line 2 and \texttt{x["3"]} in line 3 denote the array element of \texttt{x["3"]}, but \texttt{x["03"]} denotes a completely different element. So naive idea of modeling array index using integers will not work -- it cannot distinguish the indexes \texttt{"3"} and \texttt{"03"}.

If we model array index with strings, then we need to face the second problem -- we need to handle arithmetics in the array index. Let us look at the case of line 4, we need to update the value of \texttt{x["03"-1]}. The expression \texttt{"03"-1} will be evaluated to $2$, which involves an implicit type conversion from the string \texttt{"03"} to an integer value $3$ due to the \texttt{-} operation. Then the number $2$ will be converted back to string \texttt{"2"} and used as array index and hence \texttt{x["03"-1]} is the array element of \texttt{x["2"]}. Even for a simple example like this, the conversion between string and number is unavoidable. This is a rather straightforward array operation, and so this limit will cripple any model of non-trivial JavaScript code.

>>>>

Here both \texttt{x[3]} in line 2 and \texttt{x["3"]} in line 3 denote the array element of \texttt{x["3"]}, but \texttt{x["03"]} denotes a completely different element. So na\"ive idea of modeling array index with integers will not work -- it cannot distinguish the indexes \texttt{"3"} and \texttt{"03"}.

If array indexes are modeled as strings, we need to face the problem of handling of arithmetics in the array index. Let us look at the case of line 4, we need to update the value of \texttt{x["03"-1]}. The evaluation of the expression \texttt{"03"-1} involves an implicit type conversion from the string \texttt{"03"} to an integer value $3$ due to the \texttt{-} (minus) operation. The result of the evaluation of \texttt{"03"-1} is the integer $2$, which is then converted back to string \texttt{"2"} and used as the array index. Hence \texttt{x["03"-1]} means the array element of \texttt{x["2"]}. Even for a simple example like this, the conversion between string and number is unavoidable. This is a rather straightforward array operation, and so this limit will cripple any model of non-trivial JavaScript code.
